---
title: "Introduction to scAnnotatR.models"
author: "Johannes Griss"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{1. Introduction to scAnnotatR}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(rmarkdown.html_vignette.check_title = FALSE)
```

## Introduction

The **scAnnotatR.models** packages contains a set of pre-trained models to classify
various (immune) cell types in human data to be used by the `scAnnotatR` package.

`scAnnotatR` is an R package for cell type prediction on single cell 
RNA-sequencing data. Currently, this package supports data in the forms 
of a `Seurat` object or a `SingleCellExperiment` object.

If you are interested in directly applying these models to your data, please
refer to the vignettes of the `scAnnotatR` package.

## Installation

The `scAnnotatR.models` package is a `AnnotationHub` package. Normally, it
is automatically loaded by the `scAnnotatR` package.

To load the package manually into your R session, please use the Bioconductor
`AnnotationHub` package:

```{r}
# install the AnnotationHub package if needed
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

if (!requireNamespace("AnnotationHub"))
  BiocManager::install("AnnotationHub")

# use the AnnotationHub to load the scAnnotatR.models package
eh <- AnnotationHub::AnnotationHub()

# load the stored models
models <- AnnotationHub::query(eh, "scAnnotatR.models")
```

## Data Structure

The `models` object is a named list containing the cell type's name as key
and the respective classifier as value:

```{r}
# print the available cell types
names(models)
```

Each classifier is an instance of the `scAnnotatR S4 class`. For example:

```{r}
models[['B cells']]
```

## Included models

The `scAnnotatR` package comes with several pre-trained models to classify
cell types.

```{r}
# load scAnnotatR into working space
library(scAnnotatR)
```

The models are stored in the `default_models` object:

```{r}
default_models <- load_models("default")
names(default_models)
```

The `default_models` object is named a list of classifiers. Each classifier 
is an instance of the `scAnnotatR S4 class`. For example:

```{r}
default_models[['B cells']]
```

Please refer to the `scAnnotatR` package documentation for detailed information
about how to use these classifiers.

## Session Info

```{r}
sessionInfo()
```
